A weakly structured stem for human origins in Africa

### 2022-07-27 paper.tex
fix up a few references

We used \texttt{Relate} \citep{Speidel2019-nj} to infer the distribution of
coalescence rates over time in real data and data simulated from our inferred models. Many 
previous studies have found a reduction of coalescence rates 
between $1000$ka and $100$ka in humans, and thus inferred an increase 
in $N_e$ during the same period \citep{Li2011-le}.
This increase in inferred $N_e$ could be due to either an increase in population size or to 
ancestral population structure during the Middle Stone Age \citep{Mazet2015-wn}.
All models, including the
single-origin model, recapitulate an inferred ancestral
increase in $N_e$ between 100ka-1Ma extending deeper in the past than the relate estimate (Figure~\ref{fig:supp-iicr-sim} and Section \ref{inferred_relate}).
Whereas the single-origin model achieves this by
an increase in $N_e$ during that period, the best-fit model recapitulate
this pattern without corresponding population size changes.

@@

Other studies have fit tree-like demographic models to African populations using 
distributions of allele frequencies or related statistics,
finding inconsistent divergence times \cite{Henn2018, Bergstrom2021}.
Section~\ref{sec:IM-reinfer} explains this behaviour:
split times inferred using isolation with migration models and
distributions of allele frequencies simulated under our reticulated
models are highly variable and much deeper than the more recent
estimated population divergence.

>>>>

We used \texttt{Relate} \citep{Speidel2019-nj} to infer the distribution of
coalescence rates over time in real data and data simulated from our inferred
models. Many previous studies have found a reduction of coalescence rates
between $1000$ka and $100$ka in humans, and thus inferred an increase in $N_e$
during the same period \citep{Li2011-le}.  This increase in inferred $N_e$
could be due to either an increase in population size or to ancestral
population structure during the Middle Stone Age \citep{Mazet2016-wn}.  All
models, including the single-origin model, recapitulate an inferred ancestral
increase in $N_e$ between 100ka-1Ma extending deeper in the past than the
relate estimate (Figure~\ref{fig:supp-iicr-sim} and Section
\ref{inferred_relate}). Whereas the single-origin model achieves this by an
increase in $N_e$ during that period, the best-fit model recapitulate this
pattern without corresponding population size changes.

@@

Other studies have fit tree-like demographic models to African populations
using distributions of allele frequencies or related statistics, finding
inconsistent divergence times \cite{Henn2018-rf,Bergstrom2021-iw}.
Section~\ref{sec:IM-reinfer} explains this behaviour: split times inferred
using isolation with migration models and distributions of allele frequencies
simulated under our reticulated models are highly variable and much deeper than
the more recent estimated population divergence.
